Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-12 analysis/paper/paper.Rmd
knited paper.Rmd into an html doc

---
title: "Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations"
author:
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: true
  - Nicholas J. Porter:
      email: Nicholas.Porter@merck.com
      institute: [biomark]
      correspondence: false
  - Kevin E. See:
      email: Kevin.See@dfw.wa.gov
      institute: [biomark, wdfw]
      correspondence: false
  - Michael S. Hall:
      email: Mike.Hall1@merck.com
      institute: [biomark]
      correspondence: false
  - Tara E. Blackman:
      email: tara.blackman@mthoodenvironmental.com
      institute: [mhe]
      correspondence: false
  - Michael W. Ackerman:
      email: mike.ackerman@mthoodenvironmental.com
      institute: [biomark, mhe]
      correspondence: false
institute:
  - biomark: Biomark, Inc., 705 South 8th Street, Boise, Idaho, 83702, USA
  - wdfw: Washington Department of Fish and Wildife, Under A Bridge, Seattle, Washington, 00000, USA
  - mhe: Mount Hood Environmental, PO Box 4282, McCall, Idaho, 83638, USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua      
fontsize: 12pt
mainfont: Times New Roman
bibliography: 
- references.bib      # Kevin's library
- AckermanLibrary.bib # Mike's library
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
  Abstract text here. 
keywords: |
  northern pikeminnow; Chinook salmon; predation; mark-recapture; bioenergetics
highlights: |
  These are the highlights. 
---

@@

```{r schnabel-estimator, eval = F}
# using Schnabel model
N_mods = cmr_df %>%
  # filter out spring 2021 (no recapture)
  filter(event_name != "Spring_2021") %>%
  group_by(event_name, species, date) %>%
  summarise(n = n(),
            m = sum(capture_type == "Recapture", na.rm = T),
            u = sum(capture_type == "Mark" | is.na(capture_type)),
            R = sum(fish_status == "Live", na.rm = T),
            .groups = "drop") %>%
  group_by(event_name, species) %>%
  nest() %>%
  crossing(model = c("Schnabel",
                     "SchumacherEschmeyer")) %>%
  mutate(mr_model = map2(data,
                         model,
                         .f = function(x, y) {
                           with(x,
                                mrClosed(n = n,
                                         m = m,
                                         R = R,
                                         method = y,
                                         chapman.mod = TRUE))
                         }),
         N = map_dbl(mr_model,
                     .f = summary),
         CI = map(mr_model,
                  .f = confint),
         Lci = map_dbl(CI,
                       .f = function(x) x[1]), 
         Uci = map_dbl(CI,
                       .f = function(x) x[2])) %>%
  ungroup() %>%
  select(-CI)

>>>>

---
title: "Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations"
author:
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: true
  - Nicholas J. Porter:
      email: Nicholas.Porter@merck.com
      institute: [biomark]
      correspondence: false
  - Kevin E. See:
      email: Kevin.See@dfw.wa.gov
      institute: [biomark, wdfw]
      correspondence: false
  - Michael S. Hall:
      email: Mike.Hall1@merck.com
      institute: [biomark]
      correspondence: false
  - Tara E. Blackman:
      email: tara.blackman@mthoodenvironmental.com
      institute: [mhe]
      correspondence: false
  - Michael W. Ackerman:
      email: mike.ackerman@mthoodenvironmental.com
      institute: [biomark, mhe]
      correspondence: false
institute:
  - biomark: Biomark, Inc., 705 South 8th Street, Boise, Idaho, 83702, USA
  - wdfw: Washington Department of Fish and Wildife, Under A Bridge, Seattle, Washington, 00000, USA
  - mhe: Mount Hood Environmental, PO Box 4282, McCall, Idaho, 83638, USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua      
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography: 
- references.bib      # Kevin's library
- AckermanLibrary.bib # Mike's library
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
  Abstract text here. 
keywords: |
  northern pikeminnow; Chinook salmon; predation; mark-recapture; bioenergetics
highlights: |
  These are the highlights. 
---

@@

```{r schnabel-estimator, eval = T}
# using Schnabel model
N_mods = cmr_df %>%
  # filter out spring 2021 (no recapture)
  filter(event_name != "Spring_2021") %>%
  group_by(event_name, species, date) %>%
  summarise(n = n(),
            m = sum(capture_type == "Recapture", na.rm = T),
            u = sum(capture_type == "Mark" | is.na(capture_type)),
            R = sum(fish_status == "Live", na.rm = T),
            .groups = "drop") %>%
  group_by(event_name, species) %>%
  nest() %>%
  crossing(model = c("Schnabel",
                     "SchumacherEschmeyer")) %>%
  mutate(mr_model = map2(data,
                         model,
                         .f = function(x, y) {
                           with(x,
                                mrClosed(n = n,
                                         m = m,
                                         R = R,
                                         method = y,
                                         chapman.mod = TRUE))
                         }),
         N = map_dbl(mr_model,
                     .f = summary),
         CI = map(mr_model,
                  .f = confint),
         Lci = map_dbl(CI,
                       .f = function(x) x[1]), 
         Uci = map_dbl(CI,
                       .f = function(x) x[2])) %>%
  ungroup() %>%
  select(-CI)
